---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: ~/Dropbox/miscelanea/svm-r-markdown-templates/svm-latex-syllabus.tex
geometry: margin=1in

title: "PLCP: Introduction to Comparative Political Economy"
author: Robert Kubinec
date: "Fall 2018"

email: "rmk7xy@virginia.edu"
web: "www.robertkubinec.com"
officehours: "W 09:00-11:30 a.m."
office: "XXXX"
classroom: "*XXX*"
classhours: "XXX"

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2018-08-27")
# fri <- as.Date("2016-01-08")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bib <- ReadBib("C:/Users/bobku/Box Sync/TEX/bibtex/bib/misc/BibTexDatabase.bib",
                check=F)
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

```

# Course Description

Comparative political economy is the study of political institutions that control economic activity and the ramifications that these institutions have on political outcomes, including social movements, elections and legislatures. The discipline has a very rich history, dating as far back as Aristotle, but it received its current form during the 18th and 19th centuries where we will begin our course overview. Lately, research in comparative political economy has explored social and political phenomena not considered to be heavily affected by economic constraints, such as media coverage, sectarianism and the rebel group recruitment. Through this broadening of political economy, the field has become distilled into a set of principles, called rational choice, that can be applied to a wide set of social institutions. In this class, we will explore the traditional study of political-economic outcomes, including the effects of income inequality, trade, corruption and international financial institutions (IFIs), along with a summary of trending research in election fraud, one-party states, and civil wars.

# Course Objectives

1. Attain mastery of evaluation and critique of a wide range of readings in the discipline of political economy;

2. Employ the rational-choice approach in theoretical and applied settings through class discussion & writing;

3. Engage in the scholarly process of discovery through an independent research project.

# Required Texts

The following two books have been purchased and are available at the book store. I have also placed a copy of each on reserve at the library. We will spend a week on each book as intensive deep-dive into the arguments made by these authors and how they use political economy as a methodology for research.

```{r, echo = FALSE, results="asis"} 
bib["arriola2015", "tilly1992"]
``` 


# Course Policies

Please use the information below as a reference for how this class will be conducted. I would ask that you review this information before contacting me with any questions.

## Grading Policy

- **20%** of your grade will be determined by a midterm during normal class hours.

- **40%** of your grade will come from a 15-20 page (graduate: 25-30 page) paper that explores in further detail one of the research areas on the class syllabus. By the midterm students must have three hypotheses related to one of these research areas and a draft of available resources, which will constitute 5% of the 40%. I expect that students will use original data collection, whether quantitative or qualitative, to answer the questions posed.

- **20%** of your grade will be determined by your attendance and participation in class. I expect you to come having read the reading and prepared to pose at least one question or critique of the readings for that week.

- **20%** of your grade will come from three 2-page critical summaries of the reading that you must complete on three separate weeks of the class.

## Attendance Policy



## Late Arrival of the Professor Policy

My current university, from what I have been told, asks professors to have policies written into their syllabus about what students should do if the professor is more than 15 minutes late to class. This seems like an anachronism. I will inform students via e-mail in advance of class if class is cancelled for the day. I will also contact our department secretary if something happened on the way to work. Failing that, assume the worst happened to me. I ask the students make sure that my story gets the proper treatment on an *Investigation Discovery* show. I also ask that my story be narrated by Keith Morrison.

## E-mail Policy

I am usually quick to respond to student e-mails. However, student e-mails tend to do several things that try my patience. I have a new policy, effective Fall 2016, that outlines why I will not respond to certain e-mails students send. Multiple rationales follow.

1. The student could answer his/her own inquiry by reading the syllabus.
2. The student missed class for which there was no exam. I do not need to know the exact reason for a missed class. Students with excusable absences are responsible for giving me a note *in hard copy* that documents the reason for the missed class. An e-mail is unnecessary unless the impromptu absence involved missing a midterm or final.
3. The student wants to know what topics s/he missed during a class s/he skipped. The answer is always "you missed what was on the syllabus."
4. The student is protesting a grade without reference to specific points of objection. See the policy on protesting a grade in the syllabus. These e-mails tend to be expressive utility on the part of the student and do not require a response from me. Students interested in improving their knowledge of material should see me during office hours.
5. The students wants to know how many classes s/he missed at some point during the semester. I assume the student has a better answer to that question than me until the end of the semester.
6. The student is requesting an extension on an assignment for which the syllabus already established the deadline. The answer is always "no".
7. The student is ["grade grubbing"](https://www.math.uh.edu/~tomforde/GradeGrubbing.html) or asking to round up a grade. The answer is always "no".
8. The student is asking for an extra credit opportunity, a request that amounts to more grading for the professor. The answer is "no".


## Make-Up Exam Policy

There are **NO** make-ups for missed exams. Don't bother asking.

## Academic Dishonesty Policy

Don’t cheat. Don’t be that guy. Yes, you. You know exactly what I’m talking about too.

## Disabilities Policy

Federal law mandates the provision of services at the university-level to qualified students with disabilities. Make sure to include all that relevant information here.


\newpage

# Class Schedule

Students must read the following before Tuesday's class session.  Important: class readings are subject to change, contingent on mitigating circumstances and the progress we make as a class.  Students are encouraged to attend lectures and check the course website for updates. 

## `r advdate(mon, 1)`: Syllabus Day

*No class Thursday (Political scientists usually have a conference to start the semester).*

Read *all* associated documents on course website.
  
  - [Taking Good Notes](http://svmiller.com/blog/2014/09/taking-good-notes/)
  - [Dos and Dont's of Writing for Students](http://svmiller.com/blog/2015/06/dos-and-donts-of-writing-for-students/)
  - [Assorted Tips for Students on Writing Research Papers](http://svmiller.com/blog/2015/12/assorted-tips-students-research-papers/)
  - [Exam Grading Policy](https://www.dropbox.com/s/apihjs7di81aqcv/svm-exam-grading-policy.pdf?dl=0)
  - [Fun with Attendance and Grades (i.e. Students Should Attend Class)](http://svmiller.com/blog/2016/05/fun-with-attendance-grades/)
    

## `r advdate(mon, 2)`: The First Topic Where We Read John Vasquez

```{r, echo = FALSE, results="asis"} 
bib[author = "vasquez"]
``` 

##  `r advdate(mon, 3)`: Read the Nos. 90-97 Items in My Bib

```{r, echo = FALSE, results="asis"} 
bib[90:97]
``` 

*Your "Slow Ride" appreciation paper is due in Thursday's class*.

##  `r advdate(mon, 4)`: Read Bib Item No. 120

```{r, echo = FALSE, results="asis"} 
bib[120]
``` 



##  `r advdate(mon, 5)`: The Fourth Topic with Bib Item No. 510

```{r, echo = FALSE, results="asis"} 
bib[510]
``` 

##  `r advdate(mon, 6)`: Keep
##  `r advdate(mon, 7)`: Going
##  `r advdate(mon, 8)`: Down

##  `r advdate(mon, 9)`: the

##  `r advdate(mon, 10)`: Line

##  `r advdate(mon, 11)`: Until

##  `r advdate(mon, 12)`: You

## `r advdate(mon, 13)`: Are

##  `r advdate(mon, 14)`: Done

##  `r advdate(mon, 15)`: with


##  `r advdate(mon, 16)`: your


##  `r advdate(mon, 17)`: Syllabus 

